Relationships in the extremes and their influence on competition and coexistence

### 2021-10-29 paper/Paper.Rnw
trivial

\underline{paragraph summarizing results of G2 and how it compares and builds on prior theory}
Furthermore, we have shown not only that is it possible to decompose storage effect into the effect of correlation \emph{per se} and the effect of ATAs, but this new term that holds the contribution of not only the correlation but the structure of the correlation is a non-negligible term, in the lottery model. Our result adds coexistence to the list of ecological theory/phenomena that ATAs have been found to be important for \citep{Ghosh_2020_AER, Ghosh_2020_Eco, Ghosh_2020_ecolevol, Ghosh_2021}. Seemingly consistent with fluctuation dependent mechanisms, as \sigma increased, so did the the magnitudes of $\Delta_i^{[EC]}$ and $\Delta_i^{[E \nat C]}$.
%Higher sigma means a more fluctuating and variable environment. Then, if environmental fluctuations become more variable, the effect of ATAs becomes more important and non-negligible (rescue or exclusion). 
%Delta=1 means no overlapping generations -  breaking the storage effect requirement of buffered population growth.

>>>>

\underline{paragraph summarizing results of G2 and how it compares and builds on prior theory}
Furthermore, we have shown not only that is it possible to decompose storage effect into the effect of correlation \emph{per se} and the effect of ATAs, but this new term that holds the contribution of not only the correlation but the structure of the correlation is a non-negligible term, in the lottery model. Our result adds coexistence to the list of ecological theory/phenomena that ATAs have been found to be important for \citep{Ghosh_2020_AER, Ghosh_2020_Eco, Ghosh_2020_ecolevol, Ghosh_2021}. Seemingly consistent with fluctuation dependent mechanisms, as $\sigma$ increased, so did the the magnitudes of $\Delta_i^{[EC]}$ and $\Delta_i^{[E \nat C]}$.
%Higher sigma means a more fluctuating and variable environment. Then, if environmental fluctuations become more variable, the effect of ATAs becomes more important and non-negligible (rescue or exclusion). 
%Delta=1 means no overlapping generations -  breaking the storage effect requirement of buffered population growth.
